### 2021-06-03 paper/model_validation.tex
Add comment.
Adjust figures to use new results figures.

\textcolor{red}{summarize the fit}

@@

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/comparisons/fall_fit/full_new_known_case}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/comparisons/spring_fit/full_new_known_case}
\end{subfigure}
\caption{Simulated and Empirical Infections}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates.}
\label{fig:aggregated_fit}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/incidences_by_group/age_group_rki/full_fall_baseline_new_known_case}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/incidences_by_group/age_group_rki/full_spring_baseline_new_known_case}
\end{subfigure}
\caption{Simulated and Empirical Infections by Age Group}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different age groups.}
\label{fig:age_group_fit}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/incidences_by_group/state/full_fall_baseline_new_known_case}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/incidences_by_group/state/full_spring_baseline_new_known_case}
\end{subfigure}
\caption{Simulated and Empirical Infections by Age Group}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different federal regions.}
\label{fig:state_fit}
\end{figure}

>>>>

\textcolor{red}{summarize the fit; Some of this needs to go in the appendix. I suggest the age group and federal state fit goes there???}

@@

\begin{figure}[ht]
\centering
  \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
\caption{Simulated and Empirical Infections}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates.}
\label{fig:aggregated_fit}
\end{figure}

\begin{figure}[ht]
\centering
  \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/age_group_rki/full_combined_baseline_new_known_case}
\caption{Simulated and Empirical Infections by Age Group}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different age groups.}
\label{fig:age_group_fit}
\end{figure}

\begin{figure}[ht]
\centering
  \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/state/full_combined_baseline_new_known_case}
\caption{Simulated and Empirical Infections by Federal State}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different federal states.}
\label{fig:state_fit}
\end{figure}

### 2021-06-03 paper/results.tex
Adjust figures to use new results figures.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/comparisons/one_off_and_combined/full_new_known_case}
    \caption{The Effect of Each Channel on Observed New Cases Separately}
    \label{fig:}
    \figurenotes{\textcolor{red}{\ldots}}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
\end{subfigure}
\caption{The Effect of Policies on Observed and Unobserved Cases}
\label{fig:explain_decline}
\figurenotes{\textcolor{red}{\ldots}}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/placeholder}
  %../figures/results/figures/scenario_comparisons/school_scenarios/full_new_known_case
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/placeholder}
  %../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected
\end{subfigure}
\caption{The Effect of Different School Scenarios on Observed and Unobserved Cases}
\figurenotes{\textcolor{red}{K: One of the scenarios starts too early. Will be fixed with the next full simulations run.}}
\label{fig:school_scenarios}
\end{figure}

\FloatBarrier

\input{../figures/results/tables/student_infections_table}
